Analyzing Toronto's Dining Scene: Public Food Safety and Economic Indicators in Focus

### 2024-01-22 Outputs Folder 2/paper_final.qmd
Add files via upload

---
title: "Deciphering Toronto's Food Safety in Economic Context"
subtitle: "A public health environment that is constantly improving"
author: 
  - Tianen (Evan) Hao
thanks: "Code and data are available at: https://github.com/ShadyEvan4830/Tonronto_Dinesafe_DataAnalysis.git"
date: January 21, 2024
date-format: long
abstract: "This report uses the R programming language to analyze a data set of food safety inspections at Toronto dining establishments and further uses additional data sets to correlate food safety trends with an economic indicator such as the Consumer Price Index (CPI). Our analysis shows a limited reduction in sanitation infractions; this potentially means food safety compliance is improving in the City of Toronto. Additionally, the analysis suggests some potential links between economic downturns and increases in health infractions. This report is an appropriate reference resource for policymakers, and it overall highlights the inextricable relationship between economic health and public safety."
format: pdf
toc: true
number-sections: true
bibliography: bibliography.bib
---

>>>>

---
title: "Analyzing Toronto's Dining Scene: Public Food Safety and Economic Indicators in Focus"
subtitle: "A public health environment that is constantly improving"
author: 
  - Tianen (Evan) Hao
thanks: "Code and data are available at: https://github.com/ShadyEvan4830/Tonronto_Dinesafe_DataAnalysis.git"
date: January 21, 2024
date-format: long
abstract: "This report uses the R programming language to analyze a data set of food safety inspections at Toronto dining establishments and further uses additional data sets to correlate food safety trends with an economic indicator such as the Consumer Price Index (CPI). Our analysis shows a limited reduction in sanitation infractions; this potentially means food safety compliance is improving in the City of Toronto. Additionally, the analysis suggests some potential links between economic downturns and increases in health infractions. This report is an appropriate reference resource for policymakers, and it overall highlights the inextricable relationship between economic health and public safety."
format: pdf
toc: true
number-sections: true
bibliography: bibliography.bib
---
